\section{Benchmark Design}
\label{sec:benchmark}

\subsection{Runner contract}

ClinProg-Bench specifies a language-agnostic \emph{runner contract}
(\texttt{src/clinprog\_bench/runners/contract.md}, v0.1.0) that any agent
must satisfy. For each task the harness:
%
\begin{enumerate}
  \item materialises a fresh workspace populated with the task's fixtures,
  \item invokes the agent's \texttt{BaseAdapter.run(task, workspace)} method,
  \item collects a \texttt{Submission} record (immutable; outputs keyed by
        the task's \texttt{output\_kind}),
  \item passes the submission to the category-specific scorer.
\end{enumerate}
%
The contract is intentionally state\emph{ful}: the workspace persists across
sub-tasks within a multi-step task, and the contract admits multi-agent and
retrieval-augmented systems alongside single-turn LLMs.

\subsection{Scorers}

Each category has a single deterministic scorer; \emph{no} LLM-as-a-judge is
used. Scorers are pure functions of (gold output, submission), implemented
in \texttt{src/clinprog\_bench/scorers/}, and unit-tested
(\texttt{tests/scorers/}, 79 tests, 100\% pass on v0.1.0).

\begin{table}[h]
\centering
\small
\caption{Scoring rubrics per category.}
\label{tab:scorers}
\begin{tabular}{lll}
\toprule
Scorer & Method & Output range \\
\midrule
\texttt{codegen}      & AST-equivalence + slot-fill on key statements      & $[0, 1]$ \\
\texttt{log\_review}  & set match / confusion matrix on review findings    & $[0, 1]$ \\
\texttt{spec\_extract}& set match on extracted slots                       & $[0, 1]$ \\
\texttt{doc}          & slot-fill on required documentation fields         & $[0, 1]$ \\
\texttt{debug}        & patch-apply: does the patch fix the seeded defect? & $\{0, 1\}$ \\
\bottomrule
\end{tabular}
\end{table}

The aggregate benchmark score is the macro-average across the five
categories, reported alongside per-category and per-sub-category breakdowns.

\subsection{Reference baseline}

A rules-only \texttt{ReferenceBaselineAdapter}
(\texttt{src/clinprog\_bench/runners/baselines/reference.py}) emits empty
or trivially-formed submissions. Its purpose is \emph{not} comparison but
scorer validation: the reference baseline scores $0.00$ across all
categories, confirming that no scorer admits trivial outputs.

\subsection{Evaluation harness and CI}

The benchmark CI workflow (\texttt{.github/workflows/eval.yml}) runs three
jobs on every push to \texttt{master}: schema-lint, unit tests, and a
reference-baseline smoke evaluation. A successful CI run is a precondition
for tagging a release.
