\section{Introduction}
\label{sec:intro}

Clinical-trial statistical programming sits at the intersection of regulated
software, domain-specific data standards (CDISC SDTM, ADaM, Define-XML), and
high-stakes outputs: every dataset and listing in a regulatory submission is
inspected by FDA, EMA, or PMDA reviewers and feeds directly into approval
decisions. The work is also voluminous---a single phase-III trial typically
yields hundreds of programs across SAS, R, and increasingly Python---and
expensive: median compensation for clinical statistical programmers exceeds
\$120k/year and the global shortage of qualified personnel is well documented.

Despite recent advances in code generation, applying general-purpose LLMs to
clinical programming surfaces systematic failure modes that existing benchmarks
do not capture. Consider two representative errors observed when prompting
frontier models on CDISC tasks: (1)~a model asked to derive the SDTM AE domain
populates \texttt{AEBODSYS} with the verbatim term instead of the MedDRA
System Organ Class, producing a dataset that passes functional tests but
violates CDISC controlled terminology; (2)~a model generating an ADaM ADSL
dataset assigns \texttt{TRT01PN} values of \texttt{1, 2, 3} instead of the
protocol-specified \texttt{0, 54, 81}, introducing a treatment-mapping error
that would propagate through every downstream efficacy table. These failures
are invisible to general code benchmarks but would trigger regulatory
rejections. ClinProg-Bench is designed to expose precisely this class of
domain-specific correctness violations.

No existing public benchmark evaluates code LLMs or agentic systems on
clinical-programming workflows. General code benchmarks (HumanEval, MBPP,
SWE-Bench, BigCodeBench) cover algorithmic Python or open-source maintenance;
biomedical NLP benchmarks (MedQA, PubMedQA) target text understanding rather
than code; and pharma-internal evaluations rely on proprietary studies that
cannot be released. The vacuum forces practitioners to evaluate models on
hand-rolled, non-comparable test suites.

\paragraph{Contributions.}
\begin{enumerate}
  \item \textbf{ClinProg-Bench} (\S\ref{sec:dataset}): 250 expert-curated tasks
    spanning code generation, code review, specification extraction,
    documentation, and debugging, all grounded in the publicly redistributable
    CDISC SDTM/ADaM Pilot Project (CC-BY-4.0).
  \item \textbf{Deterministic scorers} (\S\ref{sec:benchmark}): five
    category-specific scorers using AST equivalence, set match, confusion
    matrix, slot fill, and patch-apply rubrics. No LLM-as-a-judge.
  \item \textbf{Stateful runner contract} (\S\ref{sec:benchmark}): a
    language-agnostic workspace protocol that admits multi-agent and
    RAG-augmented systems, not just single-turn inference.
  \item \textbf{Governance scaffolding} (\S\ref{sec:dataset}): two-channel
    leakage audit and a Cohen's $\kappa \geq 0.8$ dual-reviewer audit on a
    stratified random subset.
  \item \textbf{Public release}: Apache-2.0 / CC-BY-4.0, Zenodo DOI, CI-tested
    on every push, and a rules-only reference baseline for scorer validation.
\end{enumerate}
