\section{Limitations}
\label{sec:limitations}

\paragraph{One substrate.} ClinProg-Bench v0.1.0 is grounded entirely in the
CDISC SDTM/ADaM Pilot Project (a phase-II Alzheimer's-disease protocol).
This bounds external validity: results on Pilot01-derived tasks may not
generalise across therapeutic areas, study phases, or proprietary corporate
standards. A v0.2 release with at least one additional public substrate is
planned.

\paragraph{Scorer rigidity.} Deterministic scorers reject semantically
equivalent but syntactically divergent answers (e.g.\ a SAS \texttt{IF/THEN}
that achieves the same derivation as a \texttt{WHERE} clause). Slot-fill and
AST-equivalence rubrics mitigate but do not eliminate this. We recommend
reporting scorer-conformance error rates alongside the headline number.

\paragraph{Static gold outputs.} Gold outputs are frozen at substrate commit
\texttt{658fcc05}; downstream regulatory practice (CDISC versions, FDA
guidance) evolves. The benchmark is versioned and Zenodo-archived to make
this drift explicit.

\paragraph{Single English locale.} All prompts and specifications are in
English. Multilingual clinical-programming evaluation is left to future work.

\paragraph{Partial fixture coverage.} 42 of the 67 fixture base paths
referenced by task specifications point at files unauthored in the v1.0
substrate (15 SDTM \texttt{create\_*.R} programs for the CM, DS, EX, LB,
MH, QS, SC, SV domains, and 27 TLF mock templates including
hyphen/underscore naming-style drift). The runner silently skips
unresolvable paths, so the no-grounding baseline is unaffected, but the
+grounding macro is upper-bounded by a $40\%$ coverage gap on T2/T5.
Authoring these fixtures and a BM25 retrieval-augmented baseline are the
headline items for v0.1.1.

\paragraph{Operational variability under grounding.} GLM-4.5 with
fixture inlining incurred 7 upstream read-timeout errors out of 25
prompts, dropping its operational macro by $0.08$
(\S\ref{sec:baselines}). The benchmark records the operational outcome
rather than retrying because submission throughput under longer prompts
is itself a property worth measuring; submitters should report timeouts
and retries explicitly.
